Are we living in a depressive society?

### 2024-04-16 outputs/paper/paper.qmd
commit add the second plots in pie chart

```{r}
# Load necessary libraries
library(ggplot2)
library(dplyr)
library(gridExtra)
library(readr)

@@

# Filter data for the specific indicator
lonely_data <- data %>%
  filter(Indicator == "Adults who usually or always feel lonely")

# Function to create a plot for a given group with specified y-axis limits
create_plot <- function(data, group_name, ymax) {
  data_group <- data %>%
    filter(Group == group_name) %>%
    group_by(Time.Period.Label, Subgroup) %>%
    summarise(Value = sum(Value), .groups = "drop") %>%
    arrange(Time.Period.Label, Subgroup)

  # Add cumulative sum of Value for label positioning
  data_group <- data_group %>%
    group_by(Time.Period.Label) %>%
    mutate(label_pos = cumsum(Value) - 0.5 * Value,
           segment_size = Value)

  # Create the plot
  plot <- ggplot(data_group, aes(x = Time.Period.Label, y = Value, fill = Subgroup)) +
    geom_bar(stat = "identity", position = "stack") +
    geom_text(aes(y = label_pos, label = ifelse(segment_size > 5, Subgroup, "")), 
              position = position_stack(vjust = 0.5), 
              color = "white", family = "Times", check_overlap = TRUE, 
              size = ifelse(data_group$segment_size > 5, 3, 0)) +
    labs(title = paste(group_name),
         y = "Symptom rates (%)",
         x = NULL) +
    ylim(0, ymax) +
    theme_minimal() +
    theme(text = element_text(family = "Times"),
          axis.text.x = element_text(hjust = 1, size = 10),
          plot.title = element_text(size = 7),
          legend.position = "none")

  return(plot)
}

# Create plots for each group with specific y-axis limits
plot_age <- create_plot(lonely_data, "By Age", 100)
plot_sex <- create_plot(lonely_data, "By Sex", 30) 
plot_education <- create_plot(lonely_data, "By Education", 70)
plot_race <- create_plot(lonely_data, "By Race/Hispanic ethnicity", 70)

# Arrange plots in a 2 x 2 grid
grid_plots <- grid.arrange(plot_age, plot_sex, plot_education, plot_race, ncol = 2, nrow = 2)

# Print the arranged plots
print(grid_plots)

>>>>

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| label: fig-lonely-age-pie
#| fig-cap: "Adults who usually or always feel lonely by Age"

# Load necessary libraries
library(ggplot2)
library(dplyr)
library(readr)
library(here)

@@

# Filter data for the specific indicator and group
lonely_data <- data %>%
  filter(Indicator == "Adults who usually or always feel lonely") %>%
  filter(Group == "By Age") %>%
  group_by(Subgroup) %>%
  summarise(Value = sum(Value), .groups = "drop")

# Calculate percentages
lonely_data$Percentage <- lonely_data$Value / sum(lonely_data$Value) * 100

# Create the pie chart
pie_chart <- ggplot(lonely_data, aes(x = "", y = Percentage, fill = Subgroup)) +
  geom_bar(width = 1, stat = "identity") +
  coord_polar(theta = "y") +
  geom_text(aes(label = sprintf("%.1f%%", Percentage)), position = position_stack(vjust = 0.5),
            family = "Times", size = 4) +  # Set text font to Times and adjust size
  labs(title = "Adults who usually or always feel lonely by Age",
       x = NULL, y = NULL, fill = "Age Group") +
  theme_void() +
  theme(legend.position = "right",
        text = element_text(family = "Times"),  # Apply Times font to all text elements
        plot.title = element_text(size = 14))  # Customize plot title

# Print the pie chart
print(pie_chart)

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| label: fig-lonely-education-pie
#| fig-cap: "Adults who usually or always feel lonely by Education"

# Change filter to "By Education"
lonely_data_education <- data %>%
  filter(Indicator == "Adults who usually or always feel lonely") %>%
  filter(Group == "By Education") %>%
  group_by(Subgroup) %>%
  summarise(Value = sum(Value), .groups = "drop")

lonely_data_education$Percentage <- lonely_data_education$Value / sum(lonely_data_education$Value) * 100

pie_chart_education <- ggplot(lonely_data_education, aes(x = "", y = Percentage, fill = Subgroup)) +
  geom_bar(width = 1, stat = "identity") +
  coord_polar(theta = "y") +
  geom_text(aes(label = sprintf("%.1f%%", Percentage)), position = position_stack(vjust = 0.5),
            family = "Times", size = 4) +
  labs(title = "Adults who usually or always feel lonely by Education",
       x = NULL, y = NULL, fill = "Education Level") +
  theme_void() +
  theme(text = element_text(family = "Times"),
        plot.title = element_text(size = 14))

print(pie_chart_education)
